Contextual Combinatorial Cascading Bandits

### 2016-02-02 contextual combinatorial cascading bandits.tex
update algorithm to disjunctive

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{boring formatting information, machine learning, ICML}

@@

By Equation \eqref{eq:expectation}, we have 
$$
  \EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
Using the ridge regression of data 
$$
  \{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
  \hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
  \bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a symmetric positive definite matrix. For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$. Next we build on a good estimate of the difference between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, which states the following results.

@@

This theorem states that with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$ with confidence radius $\bbeta_t(\delta)$ under $\bV_t$ norm. 
Building on this, we can define an upper confidence bound of the expected weight of base arm $a$ by
\begin{equation}
  \label{eq:defU}
  \bU_t(a) = \min\left\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1 \right\}.
\end{equation}

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $w_{t, a} = \theta_*^{\top} x_{t,a}$ is proved in the following lemma.
\begin{lemma} %estimate of U
  \label{lem:estimateU}
  When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
  $$
    0 \leq \bU_t(a) - w_{t,a} \leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
  $$
\end{lemma}
\begin{proof}
	$w_{t,a} = \theta_*^{\top} x_{t,a}$. By Holder's inequality,
	\begin{align*}
		\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
		&\leq \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
	\end{align*}
	Then because
	\begin{align*}
		0 &\leq (\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}) - \theta_{\ast}^{\top}x_{t,a} \\
		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}
	\end{align*}
	and the definition of $\bU_t$ in \ref{lem:estimateU}, we can obtain the result.
\end{proof}

@@

Our proposed algorithm, C$^3$-UCB, is described in Algorithm \ref{alg:ConComCascade}. First, the learning agent computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ for the expected weights of all base arms in $E$. Second, the agent uses the computed UCBs, $\bU_t$, to select an action $\bA_t = \{\ba_{1}^t,..., \ba_{\abs{\bA_t}}^t \}$. Third, the user checks from the first base arm in $\bA_t$ and stops after checking the $\bO_t$-th base arm and the agents observes $\bw_t(\ba_k^t), k\leq \bO_t$. Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\bbeta_t(\delta)$. In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like $\begin{pmatrix} A\\ B\end{pmatrix}$.

@@

To state our main theorem, we need some definitions. Let $p_{t, A}$ be the {\em probability of full observation of $A$}, that is the probability of observing all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ at time $t$. In the same spirit of \cite{kveton2015combinatorial}, let $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability that an action could have all base arms observed over all time. The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm.

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity with bound $B$. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln(C_\gamma n) \right),
	\end{align}
	where $R$ is the sub-Gaussian constant and $C_{\gamma} = \sum_{k=1}^K \gamma_k^2 \leq K$.
\end{theorem}
\begin{proof}% [of Theorem \ref{thm:main}] %proof outline of main theorem
	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R^{\alpha}(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. This reduction is challenging for two reasons. First, our setting has contextual information. Second, we consider position discounts $\gamma_k, k \leq K$.

	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. Then by monotonicity and Lipschitz continuity, we have
	$$
		R^{\alpha}(t, \bA_t) \leq B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
	$$
	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms. Thus we need the following deduction.
	\begin{align*}
    	&\EE[R^{\alpha}(t, \bA_t)|\cH_t] \\
    	\qquad = &\EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
    	\qquad \leq & \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
    \end{align*}
    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next Lemma solves this issue.
    \begin{lemma}
    	\label{lem:XNormSumEst}
    	If $\lambda \geq C_{\gamma}$, then
    	$$
    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right),
    	$$
    \end{lemma}
    Then we can prove this theorem.
\end{proof}

@@

In the problem of cascading recommendation, when recommended with a list of items $\bA_t = (\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$, the user checks from the first item $\ba_{1}^t$ and then one by one in order. The checking process stops if the user selects one item or has checked all items without selecting anyone. In this case, the weight of base arm $a$ at time $t$, $\bw_{t,a} \in \{ 0, 1 \}$, is binary to indicate whether the user has selected item $a$ or not. Then the random variable $\bO_t$ satisfies
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$

The agent receives some reward if the user selects an item: if the user selects $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$. Usually the importance of the positions is decreasing: the first position is most important. So it is reasonable to assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
$$
\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t} = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t).
$$
where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feedback and the reward.

Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{align}
&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). \label{eq:OrRewardFunc}
\end{align}
Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$. So $f$ is the expected reward function and also a function of expected weights. It can be proved that $f$ satisfies the properties of monotonicity and Lipschitz continuity with bound $B=1$. (We leave all verifications in the appendix.) Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order. So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$. Then we have the following corollary.
\begin{corollary}
	\label{cor:or}
	In the problem of cascading recommendation, the expected reward function is defined in Eq.~\eqref{eq:OrRewardFunc}, where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln (C_\gamma n) \right).
	\end{align}
\end{corollary}

@@

The above formulation is on the disjunctive objective, that is, at a time step the user stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and the learning agent receives reward $\gamma_k$ as the result. Similarly, we could also consider the case of conjunctive objective. In this case, we can derive a slightly better result.

We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Eq.~\eqref{eq:expectation}. The learning agent observes all items until the first one with weight $0$. Suppose we also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.

The more items reveals, the more reward the agent should receive. It is reasonable to assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), k \leq \bO_{t}$ and receives reward $\br_{t}$:
\begin{align*}
	\br_{t} &= \begin{cases}
		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1,
	\end{cases}\\
	&=\begin{cases}
		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
	\end{cases}
\end{align*}

If we define a function $f$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
\begin{align}
	&f: \cS \times [0,1]^E \to [0,1] \nonumber \\
	&f(A,w) = \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
\label{eq:AndRewardFunc}
\end{align}
then we have $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$.

%In the problem of network transportations or sequential task processing, $p^*$ defined above might be very small. So we have the following improvements. Suppose we also consider position discount here.

In this case, we have the following improvements. Notice that in this case, given weights $w$, there is an oracle that outputs the best action. So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$.
\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{1}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, for the conjunctive objective satisfies
	\begin{align}
		R(n) \le& \frac{\sqrt{128}}{f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) \nonumber \\
		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln(C_\gamma n) \right).
	\end{align}
\end{theorem}
\begin{proof}
	We will prove it in the appendix. The main idea is that we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first. And then use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}

@@

%Our setting generalizes several existing works but not limited to them. If the expected reward $g$ of a base arm $a$ has the property of monotonicity and Lipschitz continuity with respect to $\theta_{\ast}^{\top}x_{a}$, then the conjunctive, or disjunctive, objective of those expected rewards can not be covered in

>>>>

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{combinatorial cascading bandits, context information, position discounts}

@@

By Eq.~\eqref{eq:expectation}, we have 
$$
  \EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
To estimate the expected reward, we reduce to the estimation of $\theta_{\ast}$, which can be obtained by the ridge regression on $x$ and samples of $\bw$. In details, using the ridge regression on data 
$$
  \{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
  \hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
  \bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a symmetric positive definite matrix. For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$. Next we obtain a good estimate of the difference between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, restated as follows.

@@

Thus with high probability, the estimate $\hat{\theta}$ lies in the ellipsoid centered at $\theta_*$ with confidence radius $\bbeta_t(\delta)$ under $\bV_t$ norm. 
Building on this, we can define an upper confidence bound of the expected weight for each base arm $a$ by
\begin{equation}
  \label{eq:defU}
  \bU_t(a) = \min\left\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1 \right\}.
\end{equation}

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $w_{t, a} = \theta_*^{\top} x_{t,a}$ is proved in the following lemma.
\begin{lemma} %estimate of U
  \label{lem:estimateU}
  When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
  $$
    0 \leq \bU_t(a) - w_{t,a} \leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
  $$
\end{lemma}
\begin{proof}
	Note $w_{t,a} = \theta_*^{\top} x_{t,a}$. By H\"{o}lder's inequality,
	\begin{align*}
		&\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} = \abs{[\bV_{t-1}^{1/2}(\hat{\theta}_{t-1} - \theta_{\ast})]^{\top} (\bV_{t-1}^{-1/2}x_{t,a})}\\
		\leq &~\norm{\bV_{t-1}^{1/2}(\hat{\theta}_{t-1} - \theta_{\ast})}_2 \norm{\bV_{t-1}^{-1/2}x_{t,a}}_2\\
		=&~\norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
		\leq&~ \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
	\end{align*}
	Because $1 - \theta_*^{\top} x_{t,a} \geq 0$ and
	\begin{align*}
		0 &\leq (\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}) - \theta_{\ast}^{\top}x_{t,a} \\
		&\leq 2 \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}},
	\end{align*}
	we can obtain the claimed result.
\end{proof}

@@

Based on the above analysis, we design our algorithm as follows. First, the learning agent computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ for the expected weights of all base arms in $E$. Second, the agent uses the computed UCBs, $\bU_t$, to select an action $\bA_t = \{\ba_{1}^t,..., \ba_{\abs{\bA_t}}^t \}$. Third, assume that the user checks from the first base arm in $\bA_t$ and stops after checking the $\bO_t$-th base arm and the agents observes $\bw_t(\ba_k^t), k\leq \bO_t$. Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\bbeta_t(\delta)$. Our proposed algorithm, C$^3$-UCB, is described in $\mathbf{Algorithm}$ \ref{alg:ConComCascade}. There we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like $\begin{pmatrix} A\\ B\end{pmatrix}$.

@@

To state our main theorem, we need some definitions. Let $p_{t, A}$ be the {\em probability of full observation of $A$}, that is, the probability of observing all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ at time $t$. Let $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ be the minimal probability that an action could have all base arms observed over all time. The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm.

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and $B$-Lipschitz continuity. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln(C_\gamma n) \right),
	\end{align}
	where $R$ is the sub-Gaussian constant and $C_{\gamma} = \sum_{k=1}^K \gamma_k^2 \leq K$.
\end{theorem}
The regret bound deteriorates as $p^*$ gets small. But unfortunately, this reciprocal dependence on $p^*$ is not known how to improve, even in the special case of disjunctive objective. Indeed, in that case, the bound in Section 2.3 of \cite{kveton2015combinatorial} also has a reciprocal dependence on $p^*$. However, in the special case of conjunctive objective, we will give an improved bound, like \cite{kveton2015combinatorial} does.

\begin{proof}% [of Theorem \ref{thm:main}] %proof outline of main theorem
	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R^{\alpha}(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. This reduction is challenging because of contextual information and position discounts $\gamma_k, k \leq K$.

	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. First by monotonicity and $B$-Lipschitz continuity, we can prove
	$$
		R^{\alpha}(t, \bA_t) \leq 2B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
	$$
	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms. Thus we need the following deduction.
	\begin{align*}
    	&\EE[R^{\alpha}(t, \bA_t)|\cH_t] \\
    	\qquad = &\EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
    	\qquad \leq & \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
    \end{align*}
    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms, which is in turn upper bounded by the following lemma.
    \begin{lemma}
    	\label{lem:XNormSumEst}
    	If $\lambda \geq C_{\gamma}$, then
    	$$
    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right),
    	$$
    \end{lemma}
    The claimed result thus follows.
\end{proof}

@@

In the problem of cascading recommendation, when recommended with an ordered list of items $\bA_t = (\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$, the user checks the list in that order. The checking process stops if the user selects one item or has checked all items without selecting anyone. The weight of base arm $a$ at time $t$, $\bw_{t,a}$, is a $\{0,1\}$ value indicating whether the user has selected item $a$ or not. Then the random variable $\bO_t$ satisfies
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$

If the user selects the $k$-th item, then the learning agent receives reward $\gamma_k \in [0,1]$. Usually the importance of the positions is decreasing: the first position is the most important. Based on this, we assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
If the user does not select any item, the agent gets no reward. At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives a reward
$\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t}$. It is not hard to see that $\br_t = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t)$ is the disjunctive of discounted weights,
where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feedback and the reward.

Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{align}
&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). \label{eq:OrRewardFunc}
\end{align}
It is easily verified that $\br_t = f(\bA_t, \bw_t)$ and that $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$. So $f$ is the expected reward function and also a function of expected weights. It can be proved that $f$ satisfies the properties of monotonicity and $1$-Lipschitz continuity. (All verifications are left in the Appendix.) 
%Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order. So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$. 
We have the following corollary.
\begin{corollary}
	\label{cor:or}
	In the problem of cascading recommendation, the expected reward function is defined in Eq.~\eqref{eq:OrRewardFunc}, where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln (C_\gamma n) \right).
	\end{align}
\end{corollary}

@@

The above formulation is on the disjunctive objective, that is, at each time step the user stops once she selects one item or has checked all recommended items. Similarly, we could also consider the case of conjunctive objective. In this case, we derive a slightly better result.

The Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ indicate the weight of item $a$ at time $t$ satisfying Eq.~\eqref{eq:expectation}. The learning agent observes all items until the first one with weight $0$. We also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.

The more items reveals, the more reward the agent should receive. Based on this, we assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), k \leq \bO_{t}$ and receives reward $\br_{t}$:
\begin{align*}
	\br_{t} &= \begin{cases}
		1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1,
	\end{cases}\\
	&=\begin{cases}
		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
	\end{cases}
\end{align*}

If we define a function $f$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
\begin{align}
	&f: \cS \times [0,1]^E \to [0,1] \nonumber \\
	&f(A,w) = \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
\label{eq:AndRewardFunc}
\end{align}
then it is not hard to verify that $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, \theta_{\ast}^{\top}x_t)$. Next is our result for the conjunctive objective with a slightly improved bound than Theorem \ref{thm:main}.

\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{1}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, for the conjunctive objective satisfies
	\begin{align}
		R^{\alpha}(n) \le& \frac{\sqrt{128}}{f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) \nonumber \\
		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln(n) \right).
	\end{align}
\end{theorem}
\begin{proof}
	We will prove it in the Appendix. The main idea is that we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first. And then use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}

@@

\begin{figure*}
	\centering
	\subfigure[Disjunctive, $\gamma=1$]{
		\includegraphics[height = 3 cm, width = 4 cm]{synD-T5-L100-K4-1.eps}}
	\subfigure[Disjunctive, $\gamma=0.9$]{
		\includegraphics[height = 3 cm, width = 4 cm]{synD-T5-L100-K4-9.eps}}
	\subfigure[Conjunctive, $\gamma=1$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{synC-T5-L100-K4-1.eps}}
	\subfigure[Conjunctive, $\gamma=0.9$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{synC-T5-L100-K4-9.eps}}
	\caption{Synthetic Data Set, L=100, K=4, d=10}
	\label{fig:synthetic} % 用于交叉引用
\end{figure*}
